Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
An explicit RAM
Bit-parallel

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target---we show an example in \cref{figure:subgraphexample}. This in some
ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
although we allow any vertex to be removed. We show that if
$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
filterings are still effective in pruning the initial search space and in providing additional
constraints respectively. We then show that combining these techniques leads to a practical
algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
algorithm for the maximum common induced subgraph problem.

@@

?? Bit parallel.

The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
the pattern graph, each of which has a domain containing one value for every vertex in the target
graph.

>>>>

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target---we show an example in \cref{figure:subgraphexample}. This in some
ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
although we allow any vertex to be removed. We show that if
$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
filterings are still effective in pruning the initial search space and in providing additional
constraints respectively. We then show that combining these techniques leads to a practical
algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
these instances in 64 GBytes of RAM. Finally, we show that iteratively increasing $k$ gives a
competitive algorithm for the maximum common induced subgraph problem.

@@

The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
the pattern graph, each of which has a domain containing one value for every vertex in the target
graph. The algorithm is bit-parallel: each $D_v$ is a bitset, and all graphs are stored as adjacency
matrices.
